\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-04-04 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
acknowledge Yvon Maday in the manual

\section*{Authors}
The SPECFEM3D Cartesian package was first developed by Dimitri Komatitsch and Jean-Pierre Vilotte at Institut de Physique du Globe (IPGP) in Paris, France
from 1995 to 1997 and then by Dimitri Komatitsch and Jeroen Tromp at Harvard University and Caltech, USA, starting in 1998.

>>>>

\section*{Authors}
The SPECFEM3D Cartesian package was first developed by Dimitri Komatitsch and Jean-Pierre Vilotte at Institut de Physique du Globe (IPGP) in Paris, France
from 1995 to 1997 and then by Dimitri Komatitsch and Jeroen Tromp at Harvard University and Caltech, USA, starting in 1998.
The story started on March 28, 1995, when Prof. Yvon Maday from CNRS and University of Paris, France, gave a lecture to
Dimitri Komatitsch and Jean-Pierre Vilotte at IPG about the nice properties of the spectral-element method that he had used for
other equations. We are deeply indebted and thankful to him for that.
